---
title: "Golda Meir Library Statistics Report"
params:
  fpath: C:/Users/briney/Documents/LibStats/reports/data
  periodStart: 2018-01-01 00:00:00
  periodEnd: 2018-05-30 23:59:59
output:
  pdf_document: 
    fig_width: 7
    fig_height: 3
---

<!--
## Name: LibStats_report_dept.Rmd
## Created: June 2018 by Kristin Briney
## Purpose: This Rmarkdown template will create a report for the whole library 
##          using cleaned StatBot data. Date ranges must be specified.
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(stringr)
library(lubridate)
library(knitr)

  depart <- params$dept
  pStart <-  ymd_hms(params$periodStart)
  pEnd <-  ymd_hms(params$periodEnd)

  ## Load consultation data
  
  finput <- paste(params$fpath, "Cons.csv", sep="/")
  Cons_all <- read_csv(finput)
  
  Cons <- filter(Cons_all, Cons_all$ConsDate>=pStart & Cons_all$ConsDate<=pEnd)
  Cons <- add_column(Cons, Week=week(Cons$ConsDate))
  
  ## Load presentation data
  
  finput <- paste(params$fpath, "Pres.csv", sep="/")
  Pres_all <- read_csv(finput)
  
  Pres <- filter(Pres_all, Pres_all$PresDateTime>=pStart & Pres_all$PresDateTime<=pEnd)
  Pres <- add_column(Pres, Week=week(Pres$PresDateTime))
  
  ## Load transaction data
  
  finput <- paste(params$fpath, "Trans.csv", sep="/")
  Trans_all <- read_csv(finput)
  
  Trans <- filter(Trans_all, Trans_all$TransDateTime>=pStart & 
                    Trans_all$TransDateTime<=pEnd)
  Trans <- add_column(Trans, Week=week(Trans$TransDateTime))
  
  ## Load and process Welcome Desk data
  
  finput <- paste(params$fpath, "WD.csv", sep="/")
  WD_all <- read_csv(finput)
  
  WD <- filter(WD_all, WD_all$WDDateTime>=pStart & 
                    WD_all$WDDateTime<=pEnd)
  WD <- add_column(WD, Department="NA", Course=as.integer(""), Faculty="NA", 
                   Location="Welcome Desk", after="Reference")
  WD <- add_column(WD, Week=week(WD$WDDateTime))
  WD <- rename(WD, TransDateTime=WDDateTime)

  # Add Welcome Desk data to Transactional data
  
  Trans <- bind_rows(Trans, WD)
```

### Golda Meir Library

### Time period: `r pStart` to `r pEnd`


## Transactions

__Total `r depart` transactions = `r count(Trans)`__

### Transactions by Library Division

```{r TstaffDept}
  TstaffDept <- group_by(Trans, StaffDept) %>% mutate(total=n()) %>% 
    select(StaffDept, total) %>% unique() %>% arrange(desc(total), StaffDept)
  
  kable(TstaffDept, format="latex")

```

### Transaction Patron Status

```{r TuserType}
  TuserTypes <- group_by(Trans, UserStatus) %>% mutate(total=n()) %>% 
    select(UserStatus, total) %>% unique() %>% arrange(desc(total))
  
  ggplot(data=TuserTypes, mapping=aes(x=UserStatus, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="User Status", y="Number of Transactions")
```

### Transaction Course Departments

_Departments listed if they had 2 or more transactions_

```{r Tinstruction}
  Tinstruction <- group_by(Trans, Department) %>% mutate(total=n()) %>% 
    select(Department, total) %>% unique() %>% 
    filter(total > 1  & Department != "NA") %>% arrange(desc(total), Department)

  kable(Tinstruction, format="latex")
  
```

### Transaction Type

_Transactions can be coded as multiple types, meaning the sum of the totals
in each category may exceed the total number of transactions_

```{r Ttype}
  Ttype_type <- bind_rows(tibble(Ttype="Directional"), tibble(Ttype="Informational"),
                              tibble(Ttype="Referral"), tibble(Ttype="Reference"))
  Ttype_total <- bind_rows(count(filter(Trans,Directional==TRUE)), 
                               count(filter(Trans, Informational==TRUE)),
                               count(filter(Trans, Referral==TRUE)),
                               count(filter(Trans, Reference==TRUE)))
  Ttype <- bind_cols(Ttype_type, Ttype_total)
  
  ggplot(data=Ttype, mapping=aes(x=Ttype, y=n, label=n)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="Type", y="Number of Transactions")
```

### Transaction Format

```{r Tform}
  Tform <- group_by(Trans, Format) %>% mutate(total=n()) %>% 
    select(Format, total) %>% unique() %>% 
    filter(Format=="in person/face to face" | Format=="on the phone" | Format=="over e-mail") %>% 
    arrange(desc(total))

  ggplot(data=Tform, mapping=aes(x=Format, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="Format", y="Number of Transactions")
```

### Transactions by Week of the Year

```{r TweekNum}
  TweekNum <- group_by(Trans, Week) %>% mutate(total=n()) %>% 
    select(Week, total) %>% unique() %>% arrange(Week)

  ggplot(data=TweekNum, mapping=aes(x=Week, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="Week of the Year", y="Number of Transactions")
```



## Consultations

__Total `r depart` consultations = `r count(Cons)`__

__Total number of patrons in consultations = `r tally(Cons, Count)` (average = `r as.integer(tally(Cons, Count)/count(Cons))`)__

### Consultations by Library Division

```{r CstaffDept}
  CstaffDept <- group_by(Cons, StaffDept) %>% mutate(total=n()) %>% 
    select(StaffDept, total) %>% unique() %>% arrange(desc(total), StaffDept)
  
  kable(CstaffDept, format="latex")
```

### Consultation Patron Status

```{r CuserType}
  CuserTypes <- group_by(Cons, UserStatus) %>% mutate(total=n()) %>% 
    select(UserStatus, total) %>% unique() %>% arrange(desc(total))
  
  ggplot(data=CuserTypes, mapping=aes(x=UserStatus, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="User Status", y="Number of Consultations")
```

### Consultation Course Departments

_Departments listed if they had 2 or more consultations_

```{r Cinstruction}
  Cinstruction <- filter(Cons, !is.na(Course)) %>% group_by(Department) %>% mutate(total=n()) %>% 
    select(Department, total) %>% unique() %>% 
    filter(total > 1 & Department != "NA") %>% arrange(desc(total), Department)

  kable(Cinstruction, format="latex")
```

### Patron Departments for non-Course Consultations

_Departments listed if they had 2 or more consultations_

```{r CuserDept}
  CuserDept <- filter(Cons, is.na(Course)) %>% group_by(UserDept) %>% mutate(total=n()) %>% 
    select(UserDept, total) %>% unique() %>% 
    filter(total > 1 & UserDept != "NA") %>% arrange(desc(total), UserDept)

  kable(CuserDept, format="latex")
```

### Consultation Format

```{r Cform}
  Cform <- group_by(Cons, Format) %>% mutate(total=n()) %>% 
    select(Format, total) %>% unique() %>% arrange(desc(total))

  ggplot(data=Cform, mapping=aes(x=Format, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="Format", y="Number of Consultations")
```

### Consultations by Week of the Year

```{r CweekNum}
  CweekNum <- group_by(Cons, Week) %>% mutate(total=n()) %>% 
    select(Week, total) %>% unique() %>% arrange(Week)

  ggplot(data=CweekNum, mapping=aes(x=Week, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="Week of the Year", y="Number of Consultations")
```



## Presentations

__Total `r depart` presentations = `r count(Pres)`__

__Total number of patrons in presentations = `r as.integer(tally(Pres, Count))` (average = `r as.integer(tally(Pres, Count)/count(Pres))`)__

__Total presentation time = `r as.integer(tally(Pres, Length))` minutes (average = `r as.integer(tally(Pres, Length)/count(Pres))` minutes)__

### Presentations by Library Division

```{r PstaffDept}
  PstaffDept <- group_by(Pres, StaffDept) %>% mutate(total=n()) %>% 
    select(StaffDept, total) %>% unique() %>% arrange(desc(total), StaffDept)
  
  kable(PstaffDept, format="latex")
```

### Presentation Patron Status

```{r PuserType}
  PuserType_type <- bind_rows(tibble(UserType="Undergraduates"), tibble(UserType="Graduates"),
                              tibble(UserType="FacultyStaff"), tibble(UserType="Children"),
                              tibble(UserType="HighSchool"), tibble(UserType="NonUWM"))
  PuserType_total <- bind_rows(count(filter(Pres,Undergraduates==TRUE)), 
                               count(filter(Pres, Graduates==TRUE)),
                               count(filter(Pres, FacultyStaff==TRUE)),
                               count(filter(Pres, Children==TRUE)),
                               count(filter(Pres, HighSchool)),
                               count(filter(Pres, NonUWM==TRUE)))
  PuserType <- bind_cols(PuserType_type, PuserType_total)
  
  ggplot(PuserType, mapping=aes(x=UserType, y=n, label=n)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="User Type", y="Number of Presentations")
```

### Presentation Course Departments

_Departments listed if they had 2 or more presentations_

```{r Pinstruction}
  Pinstruction <- group_by(Pres, Department) %>% mutate(total=n()) %>% 
    select(Department, total) %>% unique() %>% 
    filter(total > 1 & Department != "NA") %>% arrange(desc(total), Department)

  kable(Pinstruction, format="latex")
```

<!-- ### Presentation User Count

```{r Pcount}
  Pcount <- group_by(Pres, Count) %>% mutate(total=n()) %>% 
    select(Count, total) %>% unique() %>% arrange(Count)

  ggplot(data=Pcount) +
    geom_point(mapping=aes(x=Count, y=total)) +
    geom_smooth(mapping=aes(x=Count, y=total), se=FALSE) +
    labs(x="Number of Attendees", y="Number of Presentations")
``` 
-->

### Presentation Type

```{r Ptype}
  Ptype <- group_by(Pres, PresType) %>% mutate(total=n()) %>% 
    select(PresType, total) %>% unique() %>% arrange(desc(total))

  ggplot(data=Ptype, mapping=aes(x=PresType, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="Presentation Type", y="Number of Presentations")
```

### Presentation Format

```{r Pform}
  Pform <- group_by(Pres, Format) %>% mutate(total=n()) %>% 
    select(Format, total) %>% unique() %>% arrange(desc(total))

  ggplot(data=Pform, mapping=aes(x=Format, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="Format", y="Number of Presentations")
```

### Presentations by Week of the Year

```{r PweekNum}
  PweekNum <- group_by(Pres, Week) %>% mutate(total=n()) %>% 
    select(Week, total) %>% unique() %>% arrange(Week)

  ggplot(data=PweekNum, mapping=aes(x=Week, y=total, label=total)) +
    theme_light() + 
    theme(legend.position="none") +
    geom_col(fill="#999999") + 
    geom_text() +
    labs(x="Week of the Year", y="Number of Presentations")
```
